Improving the Image Acquisition Rate of an Atomic Force Microscope Through Compressive Sampling

### 2019-06-06 latex/afm-cs-main.tex
Make z-axis o.l. and c.l colors consistent with xy.

% =========================================================================
\section{Control}\label{sec:control}
The control structure for each axis is similar and essentially consists of a set of filters in series with a PI controller. The open-loop frequency response for the $Z$-axis is shown in Fig.~\ref{fig:z_control} (red curve) and in Fig.~\ref{fig:mimo_frf_uxuy} for the $X$ and $Y$ axes (black curves). The first resonance of each axis is the bending mode. For the $Z$ axis, this resonance is at 215~Hz and at approximately 350~Hz for the $X$ and $Y$ axes.

>>>>

% =========================================================================
\section{Control}\label{sec:control}
The control structure for each axis is similar and essentially consists of a set of filters in series with a PI controller. The open-loop frequency response for the $Z$-axis is shown in Fig.~\ref{fig:z_control} (black curve) and in Fig.~\ref{fig:mimo_frf_uxuy} for the $X$ and $Y$ axes (red curves). The first resonance of each axis is the bending mode. For the $Z$ axis, this resonance is at 215~Hz and at approximately 350~Hz for the $X$ and $Y$ axes.
